### 2021-03-23 input/proposal.tex
wip on implem mostly

\subsection{Dynamic partitions}
At any time, a process can become a source, hence adding a new
partition to the system. This partition eventually includes all
processes that are closer from this new source than any other else. We
described such protocol in Section~\ref{sec:scoped}. Processes
naturally converge towards their respective best partition by only
piggybacking a monotonically increasing distance in forwarded
messages. % \TODO{Traffic of each partition is contained to the
%  partition.}

@@

\noindent Figure~\ref{fig:proofB} shows that removing stale control
information is even more complex. The removal must reach all processes
of the previous shortest path going from $d$ to $b''$. Label I shows
the most obvious issue where Process $e$ changed partition for a
better but stale $\alpha_f$. Since it can remember its previous
deliveries, it could still forward $\delta_d$ for the sake of
consistency. However, this would lead to every process forwarding
every $\delta$ they ever delivered. Such protocol's overhead would
depend on past partitioning instead of current one. Label III shows
the issue when the blocking partition is already known to be stale at
Process $b'$. Process $b''$ eventually receives $\alpha_f$ from
$e$. However, it cannot deliver it, for it would break last win order.
Process $b'$ may be in an inconsistent state. Label IV shows the
corollary issue: Process $b''$ delivered a message from a process that
may be inconsistent without knowing it.

@@

\begin{proof}
\TODO{Meow meow meow.}
\end{proof}

\subsection{Dynamic networks}
Adding new communication links to the network may create shortcuts
between processes. Both processes must send their current best
partition to each other. Upon receipt, they act normally: if a process
finds out that the received partition is closer than its current one,
it delivers it which in turns also triggers another competition
amongst neighbors due to forwarding.

@@

\TODO{Move everything related to implementation here, including optimizations.}

Since the number of partitions does not monotonically increase in the
system any longer, each process requires a vector of versions that
monotonically increases over delivered operations.

This allows processes to quickly discard stale messages saving
bandwidth. For instance, a process that received a message originated
at Process $a$ with a version $2$ knows that any message originated at
Process $a$ with a version $1$ are stale system-wide; it must not
forward it. As consequence, this also ensure termination, for
corresponding add and delete messages cannot follow each other in
infinite loops.
% In terms of traffic, this only requires each message
% to piggyback a source identifier and version number.

\TODO{Paths and \NAME synergies well, for paths tend to be smaller as the
number of sources increase in the system.}

@@

\section{Complexity}
\label{sec:complexity}

>>>>

\subsection{Principle}
At any time, a process can become a source, hence adding a new
partition to the system. This partition eventually includes all
processes that are closer from this new source than any other else. We
described such protocol in Section~\ref{sec:scoped}. Processes
naturally converge towards their respective best partition by only
piggybacking a monotonically increasing distance in forwarded
messages. % \TODO{Traffic of each partition is contained to the
%  partition.}

@@

\noindent Figure~\ref{fig:proofB} shows that removing stale control
information is even more complex. The removal must reach all processes
of the previous shortest path going from $d$ to $b''$. Label I' shows
the most obvious issue where Process $e$ changed partition for a
better but stale $\alpha_f$. Since it can remember its previous
deliveries, it could still forward $\delta_d$ for the sake of
consistency. However, this would lead to every process forwarding
every $\delta$ they ever delivered. Such protocol's overhead would
depend on past partitioning instead of current one. Label III shows
the issue when the blocking partition is already known to be stale at
Process $b'$. Process $b''$ eventually receives $\alpha_f$ from
$e$. However, it cannot deliver it, for it would break last win order.
Process $b'$ may be in an inconsistent state. Label IV shows the
corollary issue: Process $b''$ delivered a message from a process that
may be inconsistent without knowing it.

@@

\begin{proof}
  \TODO{Meow meow meow.}
  \TODO{Label I: default propagation to what seems the border of the partition but isn't.}
  \TODO{Label II: gates eventually break because of I', III, IV.}
  \TODO{Label I': as Label I.}
  \TODO{Label III: detecting possible inconsistent partitioning.}
  \TODO{Label IV: propagation of this issue to all and only concerned parties.}
\end{proof}

Algorithm~\ref{algo:adddelundo} provides the instructions that
implement dynamic consistent partitioning:
\begin{inparaenum}[(i)]
\item most of the time, it propagates $\alpha$'s and $\delta$'s when
  the partitions allow it;
\item sometimes, it detects possible inconsistent partitioning and
\item solves it using propagation trees (as opposed to propagation
  graphs);
\item when required, it triggers competitions among neighboring
  partitions.
\end{inparaenum}

\paragraph{Dynamic partitions.}
We extend Algorithm~\ref{algo:add} to enable each source to revoke its
self-appointed status of source and become a simple process again. In
that regard, we enforce the delivery order of messages at each
process.

\noindent To implement last win order, each process maintains a vector
of versions that associates to each known source, or has-been source,
its known local counter. It enables processes to deliver only
up-to-date $\alpha$'s that may improve their best known partition (see
Line~\ref{line:detectA}), but also to detect possible inconsistent
partitioning (see Line~\ref{line:detectB}) as labeled by III in
Figure~\ref{fig:proofB}. From a global perspective, it ensures
monotonic increase of knowledge despite the non-monotonic number of
sources. In turns, it contributes to convergence and termination, for
corresponding $\alpha$ and $\delta$ cannot follow each other in an
infinite loop.

\noindent Upon possible inconsistency, the detecting process must
remove all $\alpha$ messages originating from it, as labeled by IV in
Figure~\ref{fig:proofB}. Contrarily to delete operations, this applies
to a sub-partition of the current partition, and cannot rely on local
counters to operate. Therefore, we implement this behavior by
piggybacking paths in messages.  \TODO{Paths and \NAME synergies well,
  for paths tend to be smaller as the number of sources increase in
  the system.}

\paragraph{Dynamic network.}
Adding new communication links to the network may create shortcuts
between processes. Both processes must send their current best
partition to each other. Upon receipt, they act normally: if a process
finds out that the received partition is closer than its current one,
it delivers it which in turns also triggers another competition
amongst neighbors due to forwarding.

@@

\paragraph{Bloom filters.}
We also propose an implementation that further decreases generated
traffic and improves on anonymity~\cite{whitaker2002forwarding}.
\NAME makes extensive use of paths to enable deleting messages without
incrementing local counters. Messages carry their respective path and
processes detect when such messages have been looping when they carry
their identity (see Lines~\ref{line:notloopingA} and
\ref{line:notloopingB} of Algorithm~\ref{algo:adddelundo}). Since
membership is all that matters, we propose to trade vectors of
identities for Bloom filters~\cite{almeida2007scalable}. Processes
know with high probability if they already received and forwarded each
message without knowing the identity of all processes that received
it.  False positive probability only incurs premature stopping of
broadcast messages and does not invalidate the delete of specific
messages.

@@

\subsection{Complexity}
\label{sec:complexity}
